---
title: <center><font size="6"><b>Variation in vocal behavior under varying stress levels</b></font></center>
subtitle: <center><font size="4"><b>Budgie INBRE stress and contact calls</b></font></center>
author: <center><font size="4"><a href="http://marceloarayasalas.weebly.com/">Marcelo Araya-Salas, PhD</a> & <a href="https://wrightbehaviorlab.org/">Timothy Wright, PhD</a></font></center>
date: <center>`r format(Sys.Date(), "%d-%m-%Y")`</center>
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 3
    df_print: kable
    toc_float:
      collapsed: yes
      smooth_scroll: yes
fontsize: 12pt 
editor_options: 
  chunk_output_type: console
---

### Load packages
```{r packages, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

## add 'developer' to packages to be installed from github
x <- c("remotes", "lubridate", "readxl", "pbapply", "viridis", "ggplot2", "kableExtra", "knitr", "formatR", "randomForest", "Rtsne", "MASS", "adehabitatHR", "sp", "GGally", "spatstat", "raster", "vegan", "brms", "lme4", "dplyr", "purrr", "forcats", "tidyr", "modelr", "tidybayes", "cowplot", "ggrepel", "posterior", "ggridges", "maRce10/PhenotypeSpace")

aa <- lapply(x, function(y) {
  
  # get pakage name
  pkg <- strsplit(y, "/")[[1]]
  pkg <- pkg[length(pkg)]
  
  # check if installed, if not then install 
  if (!pkg %in% installed.packages()[,"Package"])  {

      if (grepl("/", y))  remotes::install_github(y, force = TRUE) else
    install.packages(y) 
    }

  # load package
  a <- try(require(pkg, character.only = T), silent = T)

  if (!a) remove.packages(pkg)
  })

```

### Functions and global parameters
```{r functions and parameters, eval = TRUE, echo = TRUE}

opts_knit$set(root.dir = "..")

# set evaluation false
opts_chunk$set(fig.width = 10, fig.height = 6, warning = FALSE, message = FALSE, tidy = TRUE)

read_excel_df <- function(...) data.frame(read_excel(...))


# for reading months in english format
sl <- Sys.setlocale(locale = "en_US.UTF-8")


cols <- viridis(10, alpha = 0.7)

 summary_brm_model <- function(x){
  
   summ <- summary(x)$fixed
  fit <- x$fit  
  betas <- grep("^b_", names(fit@sim$samples[[1]]), value = TRUE)  
  hdis <- t(sapply(betas, function(y)   hdi(fit@sim$samples[[1]][[y]]))
)
  summ_table <- data.frame(summ, hdis, iterations = attr(fit, "stan_args")[[1]]$iter, chains = length(attr(fit, "stan_args")))
  summ_table <- summ_table[rownames(summ_table) != "Intercept", c("Estimate", "Rhat", "Bulk_ESS", "l.95..CI", "u.95..CI", "iterations", "chains")]
  
  summ_table <- as.data.frame(summ_table)  
  summ_table$Rhat <- round(summ_table$Rhat, digits = 3)  
  summ_table$CI_low <- round(unlist(summ_table$l.95..CI), digits = 3)  
  summ_table$CI_high <- round(unlist(summ_table$u.95..CI), digits = 3)  
  summ_table$l.95..CI <- summ_table$u.95..CI <- NULL
  
    out <- lapply(betas, function(y)  data.frame(variable = y, value = sort(fit@sim$samples[[1]][[y]], decreasing = FALSE)))
  
  posteriors <- do.call(rbind, out)
  posteriors <- posteriors[posteriors$variable != "b_Intercept", ]
  
   gg <- ggplot(data = posteriors, aes(y = variable, x = value, fill = stat(quantile))) + 
  geom_density_ridges_gradient(quantile_lines = TRUE, quantile_fun = HDInterval::hdi,  vline_linetype = 2) + 
  theme_classic() + 
     xlim(c(min(summ_table[ , "CI_low"]), max(summ_table[ , "CI_high"]))) +
  geom_vline(xintercept = 0, col = "red") + 
  scale_fill_manual(values = c("transparent", "lightblue", "transparent"), guide = "none") + ggtitle(x$formula)

  
  summ_table$Rhat <- ifelse(summ_table$Rhat > 1.05, cell_spec(summ_table$Rhat, "html", color ="white", background = "red", bold = TRUE,  font_size = 12),  cell_spec(summ_table$Rhat, "html"))
  
  signif <- summ_table[,"CI_low"] * summ_table[,"CI_high"] > 0
  
  df1 <- kbl(summ_table, row.names = TRUE, escape = FALSE, format = "html", digits = 3)
    
  df1 <- row_spec(kable_input = df1,row =  which(summ_table$CI_low * summ_table$CI_high > 0), background = adjustcolor(cols[9], alpha.f = 0.3))

  df1 <- kable_styling(df1, bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, font_size = 12)
  
  print(df1)
  
  print(gg)

  }
  
```

```{r read detections and prepare data, eval = TRUE}

# read ext sel tab calls
sels <- read.csv("./data/processed/tailored_budgie_calls_sel_tab.csv")

# keep only spectrographic parameters
sels <- sels[ , c("sound.files", "selec", "duration", "meanfreq", "sd", "freq.median", "freq.IQR", "time.IQR", "skew",  "kurt", "sp.ent", "time.ent", "entropy", "meandom", "mindom", "maxdom", "dfrange",  "modindx", "meanpeakf")]

sels$ID <- sapply(sels$sound.files, function(x) strsplit(x, "_")[[1]][1])
sels$month <- sapply(sels$sound.files, function(x) strsplit(x, "_")[[1]][2])
sels$day <- sapply(sels$sound.files, function(x) strsplit(x, "_")[[1]][3])
sels$year <- sapply(sels$sound.files, function(x) strsplit(x, "_")[[1]][4])

sels$date <- paste(sels$day, substr(sels$month, 0, 3), sels$year, sep = "-")

sels$date <- as.Date(sels$date, format = "%d-%b-%Y")

```

## Counts per individual
```{r read detections and prepare data counts, eval = TRUE, results='asis'}

df <- as.data.frame(table(sels$ID))

names(df) <- c("ID", "Sample_size")

df <- df[order(df$Sample_size, decreasing = FALSE), ]

kb <-kable(df, row.names = FALSE) 
  
kb <- kable_styling(kb, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
  
print(kb)

```

## Add metadata
```{r, eval = TRUE}

metadat <- read_excel_df("./data/raw/INBREStress_MasterDataSheet_14Nov19.xlsx")

# head(metadat)

sels$ID[sels$ID == "125YGMM"] <- "125YGHM"
sels$ID[sels$ID == "394YBHM"] <- "394WBHM"

# setdiff(sels$ID, metadat$Bird.ID) setdiff(metadat$Bird.ID, sels$ID)

sels$treatment <- sapply(1:nrow(sels), function(x) {

    metadat$Treatment[metadat$Bird.ID == sels$ID[x]][1]

})


sels$treatment.room <- sapply(1:nrow(sels), function(x) {

    metadat$Treatment.Room[metadat$Bird.ID == sels$ID[x]][1]

})


sels$round <- sapply(1:nrow(sels), function(x) {

    metadat$Round[metadat$Bird.ID == sels$ID[x]][1]

})

sels$source.room <- sapply(1:nrow(sels), function(x) {

    metadat$Source.Room[metadat$Bird.ID == sels$ID[x]][1]

})

sels$record.group <- sapply(1:nrow(sels), function(x) {

    metadat$Record.Group[metadat$Bird.ID == sels$ID[x]][1]

})


# add week
out <- lapply(unique(sels$round), function(x) {

    Y <- sels[sels$round == x, ]

    min_date <- min(Y$date)
    week_limits <- min_date + seq(0, 100, by = 7)

    Y$week <- NA
    for (i in 2:length(week_limits)) Y$week[Y$date >= week_limits[i - 1] & Y$date <
        week_limits[i]] <- i - 1

    return(Y)
})

sels <- do.call(rbind, out)


sels$cort.baseline <- sapply(1:nrow(sels), function(x) {

    if (sels$week[x] == 1)
        out <- metadat$D3.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 2)
        out <- metadat$D7.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 3)
        out <- metadat$D14.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 4)
        out <- metadat$D21.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 5)
        out <- metadat$D28.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    return(out)
})


sels$cort.stress <- sapply(1:nrow(sels), function(x) {

    if (sels$week[x] == 1)
        out <- metadat$D3.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 2)
        out <- metadat$D7.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 3)
        out <- metadat$D14.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 4)
        out <- metadat$D21.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 5)
        out <- metadat$D28.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    return(out)
})

sels$stress.response <- sels$cort.stress - sels$cort.baseline

sels$weight <- sapply(1:nrow(sels), function(x) {

    if (sels$week[x] == 1)
        out <- metadat$D3.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 2)
        out <- metadat$D7.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 3)
        out <- metadat$D14.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 4)
        out <- metadat$D21.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 5)
        out <- metadat$D28.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    return(out)
})


sels$breath.count <- sapply(1:nrow(sels), function(x) {

    if (sels$week[x] == 1)
        out <- metadat$D3.Breath.Count[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 2)
        out <- metadat$D7.Breath.Count[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 3)
        out <- metadat$D14.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 4)
        out <- metadat$D21.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 5)
        out <- metadat$D28.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    return(out)
})


# remove week 5
sels <- sels[sels$week != 5, ]

```

# Exploratory graph

## Physiological parameters
```{r, fig.width = 16, fig.height = 10, eval = TRUE}

breath.count <- stack(metadat[, c("D3.Breath.Count", "D7.Breath.Count", "D14.Breath.Count",
    "D21.Breath.Count", "D28.Breath.Count")])

weight <- stack(metadat[, c("D3.Bird.Weight..g.", "D7.Bird.Weight..g.", "D14.Bird.Weight..g.",
    "D21.Bird.Weight..g.", "D28.Bird.Weight..g.")])

cort.stress <- stack(metadat[, c("D3.CORT.Stress", "D7.CORT.Stress", "D14.CORT.Stress",
    "D21.CORT.Stress", "D28.CORT.Stress")])

cort.baseline <- stack(metadat[, c("D3.CORT.Baseline", "D7.CORT.Baseline", "D14.CORT.Baseline",
    "D21.CORT.Baseline", "D28.CORT.Baseline")])


stress <- data.frame(metadat[, c("Bird.ID", "Treatment", "Round", "Treatment.Room")],
    week = breath.count$ind, breath.count = breath.count$values, weight = weight$values,
    cort.stress = cort.stress$values, cort.baseline = cort.baseline$values, stress.response = cort.stress$values -
        cort.baseline$values)

# head(stress)

stress$week <- factor(sapply(strsplit(as.character(stress$week), "\\."), "[[", 1),
    levels = c("D3", "D7", "D14", "D21", "D28"))

stress$day <- as.numeric(gsub("D", "", as.character(stress$week)))
stress$round <- paste("Round", stress$Round)

stress$treatment <- factor(stress$Treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

# remove 5th week
stress <- stress[stress$week != "D28", ]


stress_l <- lapply(stress$Bird.ID, function(x) {
    X <- stress[stress$Bird.ID == x, ]

    X$breath.count <- X$breath.count - X$breath.count[X$week == "D3"]
    X$weight <- X$weight - X$weight[X$week == "D3"]
    X$cort.stress <- X$cort.stress - X$cort.stress[X$week == "D3"]
    X$cort.baseline <- X$cort.baseline - X$cort.baseline[X$week == "D3"]
    X$stress.response <- X$stress.response - X$stress.response[X$week == "D3"]

    return(X)
})

stress <- do.call(rbind, stress_l)

ggplot(data = stress, aes(x = day, y = weight, group = Bird.ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Weight (g)", x = "Day sample was taken") +
    theme_classic(base_size = 30) + scale_x_continuous(breaks = c(3, 7, 14, 21, 28),
    labels = c(3, 7, 14, 21, 28)) + theme(legend.position = c(0.8, 0.25))

ggplot(data = stress, aes(x = day, y = breath.count, group = Bird.ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Breath count", x = "Day sample was taken") +
    theme_classic(base_size = 30) + scale_x_continuous(breaks = c(3, 7, 14, 21, 28),
    labels = c(3, 7, 14, 21, 28)) + theme(legend.position = c(0.8, 0.25))

ggplot(data = stress, aes(x = day, y = cort.baseline, group = Bird.ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Baseline CORT", x = "Day sample was taken") +
    theme_classic(base_size = 30) + scale_x_continuous(breaks = c(3, 7, 14, 21, 28),
    labels = c(3, 7, 14, 21, 28)) + theme(legend.position = c(0.8, 0.25))

ggplot(data = stress, aes(x = day, y = cort.stress, group = Bird.ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Stress CORT", x = "Day sample was taken") +
    theme_classic(base_size = 30) + scale_x_continuous(breaks = c(3, 7, 14, 21, 28),
    labels = c(3, 7, 14, 21, 28)) + theme(legend.position = c(0.8, 0.25))

ggplot(data = stress, aes(x = day, y = stress.response, group = Bird.ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Stress response", x = "Day sample was taken") +
    theme_classic(base_size = 30) + scale_x_continuous(breaks = c(3, 7, 14, 21, 28),
    labels = c(3, 7, 14, 21, 28)) + theme(legend.position = c(0.8, 0.25))

# stress_l <- lapply(unique(stress$Bird.ID), function(x){ X <-
# stress[stress$Bird.ID == x, ] X$cort.baseline.change <- X$cort.baseline - X$
# })

standard_error <- function(x) sd(x)/sqrt(length(x))

agg_stress <- aggregate(cort.baseline ~ week + treatment, stress, mean)
agg_stress$se <- aggregate(cort.baseline ~ week + treatment, stress, standard_error)[,
    3]
agg_stress$Week <- 1:4

ggplot(data = agg_stress, aes(x = Week, y = cort.baseline, fill = treatment)) + geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = cort.baseline - se, ymax = cort.baseline + se), width = 0.1) +
    # geom_line(size = 1.2) +
scale_fill_viridis_d(begin = 0.1, end = 0.9) + facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Baseline CORT", x = "Week") + theme_classic(base_size = 30) + 
theme(legend.position = "none")
```

## FOXP2
```{r, eval = FALSE}

foxp2 <- read.csv("./data/raw/stress_IHC_counts.csv")

foxp2$Treatment[grep("HIGH", foxp2$Treatment)] <- "High stress"
foxp2$Treatment[grep("Control", foxp2$Treatment, ignore.case = T)] <- "Control"
foxp2$Treatment[grep("MED", foxp2$Treatment)] <- "Medium stress"

foxp2$Treatment <- factor(foxp2$Treatment, levels = c("Control", "Medium stress",
    "High stress"))

ggplot(data = foxp2, aes(x = Treatment, y = FoxP2.Counts.MMSt.Striatum, fill = Treatment)) +
    geom_boxplot() + geom_point() + 
scale_fill_viridis_d(begin = 0.1, end = 0.9) + 
labs(y = "% FoxP2 expression", x = "Treatment") + theme_classic(base_size = 30) +
    # scale_x_discrete( labels = c(1:4)) +
theme(legend.position = "none")
```


# Behavioral parameters
## Call counts per treatment

```{r}

call_count <- aggregate(selec ~ week + treatment + round, data = sels, length)
call_count$Week <- factor(call_count$week, levels = (unique(call_count$week))[5:1])

call_count$round <- paste("Round", call_count$round)

call_count$treatment <- factor(call_count$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

call_count$stress.response <- aggregate(selec ~ week + treatment + round, data = sels, mean)[, 4] 

ggplot(data = call_count, aes(x = treatment, y = selec, fill = Week)) + geom_bar(stat = "identity") +
    scale_fill_viridis_d(begin = 0.1, end = 0.9) + coord_flip() + facet_wrap(~round,
    ncol = 2) + labs(y = "Number of calls", x = "Treatment") + theme_classic(base_size = 30) +
    theme(legend.position = c(0.8, 0.15))
```

```{r}

call_count2 <- aggregate(selec ~ week + treatment + round + ID, data = sels, length)
agg_count <- aggregate(selec ~ week + treatment, call_count2, mean)
agg_count$se <- aggregate(selec ~ week + treatment, call_count2, standard_error)[,
    3]

agg_count$treatment <- factor(agg_count$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

ggplot(data = agg_count, aes(x = week, y = selec, fill = treatment)) + geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = selec - se, ymax = selec + se), width = 0.1) + scale_fill_viridis_d(begin = 0.1, end = 0.9) + facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Number of calls", x = "Week") + theme_classic(base_size = 30) + theme(legend.position = "none")
```


## Call counts per bird and treatment
```{r, eval = TRUE}

# Call counts per treatment by individual (in color)

call_count <- aggregate(selec ~ week + treatment + round + ID, data = sels, length)
call_count$Week <- factor(call_count$week, levels = (1:5))

call_count$round <- paste("Round", call_count$round)

call_count$treatment <- factor(call_count$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

ggplot(data = call_count, aes(x = week, y = selec, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Call count", x = "Week") +
    theme_classic(base_size = 30) + theme(legend.position = c(0.8, 0.25))
```

Acoustic parameters
```{r}

call_week_params <- aggregate(cbind(duration, meanfreq, sd, freq.median, freq.IQR,
    time.IQR, skew, kurt, sp.ent, time.ent, entropy, meandom, mindom, maxdom, dfrange,
    modindx, meanpeakf) ~ week + treatment + round, data = sels, mean)

call_week_params_sd <- aggregate(cbind(duration, meanfreq, sd, freq.median, freq.IQR,
    time.IQR, skew, kurt, sp.ent, time.ent, entropy, meandom, mindom, maxdom, dfrange,
    modindx, meanpeakf) ~ week + treatment + round, data = sels, sd)

names(call_week_params_sd) <- names(call_week_params) <- c("week", "treatment", "round",
    "Duration", "Mean_frequency_(kHz)", "SD_frequency_(kHz)", "Median_frequency_(kHz)",
    "Interquantile_frequency_range_(kHz)", "Interquantile_time_range_(s)", "Skewness",
    "Kurtosis", "Spectral_entropy", "Time_entropy", "Overall entropy", "Mean_dominant_frequency_(kHz)",
    "Minimum_dominant_frequency_(kHz)", "Maximum_dominant_frequency_(kHz)", "Dominant_frequency_range_(kHz)",
    "Modulation_index", "Mean_peak_frequency_(kHz)")


call_week_params_sd <- call_week_params_sd[, c("Duration", "Mean_frequency_(kHz)",
    "SD_frequency_(kHz)", "Median_frequency_(kHz)", "Interquantile_frequency_range_(kHz)",
    "Interquantile_time_range_(s)", "Skewness", "Kurtosis", "Spectral_entropy", "Time_entropy",
    "Overall entropy", "Mean_dominant_frequency_(kHz)", "Minimum_dominant_frequency_(kHz)",
    "Maximum_dominant_frequency_(kHz)", "Dominant_frequency_range_(kHz)", "Modulation_index",
    "Mean_peak_frequency_(kHz)")]

names(call_week_params_sd) <- paste(names(call_week_params_sd), "sd", sep = ".")


call_week_params <- cbind(call_week_params, call_week_params_sd)
call_week_params$round <- paste("Round", call_week_params$round)
call_week_params$treatment <- factor(call_week_params$treatment, levels = c("Control",
    "Medium Stress", "High Stress"))


pd <- position_dodge(0.3)

ggs <- lapply(c("Duration", "Mean_frequency_(kHz)", "SD_frequency_(kHz)", "Median_frequency_(kHz)",
    "Interquantile_frequency_range_(kHz)", "Interquantile_time_range_(s)", "Skewness",
    "Kurtosis", "Spectral_entropy", "Time_entropy", "Overall entropy", "Mean_dominant_frequency_(kHz)",
    "Minimum_dominant_frequency_(kHz)", "Maximum_dominant_frequency_(kHz)", "Dominant_frequency_range_(kHz)",
    "Modulation_index", "Mean_peak_frequency_(kHz)"), function(i) {
    call_week_params$var <- call_week_params[, i]
    call_week_params$var.min <- call_week_params$var - call_week_params[, paste(i,
        "sd", sep = ".")]
    call_week_params$var.max <- call_week_params$var + call_week_params[, paste(i,
        "sd", sep = ".")]

    ggplot(call_week_params, aes(x = week, y = var, col = treatment)) + geom_point(size = 4,
        position = pd) + geom_errorbar(aes(ymin = var.min, ymax = var.max), width = 0.3,
        position = pd, size = 1.7) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
        facet_wrap(~round, ncol = 2) + labs(y = i, x = "Week") + theme_classic(base_size = 30) +
        theme(legend.position = c(0.8, 0.25))
})

ggs
```

## Acoustic space projection

```{r, eval = FALSE}

scale_acous_param <- scale(sels[, c("duration", "meanfreq", "sd", "freq.median",
    "freq.IQR", "time.IQR", "skew", "kurt", "sp.ent", "time.ent", "entropy", "meandom",
    "mindom", "maxdom", "dfrange", "modindx", "meanpeakf")])

urfmod <- randomForest(x = scale_acous_param, importance = TRUE, proximity = TRUE,
    ntree = 10000)

saveRDS(urfmod, "./data/processed/unsupervised_random_forest_model_budgie_calls_stress_jun_2021.RDS")

mds_urf_prox <- cmdscale(1 - urfmod$proximity, k = 2)

saveRDS(mds_urf_prox, "./data/processed/MDS_unsupervised_random_forest_model_budgie_calls_stress_jun_2021.RDS")
```

Random forest
```{r}

urfmod <- readRDS("./data/processed/unsupervised_random_forest_model_budgie_calls_stress_jun_2021.RDS")

mds_urf_prox <- readRDS("./data/processed/MDS_unsupervised_random_forest_model_budgie_calls_stress_jun_2021.RDS")

sels$MDS1 <- mds_urf_prox[, 1]
sels$MDS2 <- mds_urf_prox[, 2]

print(1- sum(urfmod$votes[,1] > urfmod$votes[,2])/ nrow(urfmod$votes))
```

Proportion of real data classified as synthetic data by the unsupervised random forest: 0.005058

```{r}


ggplot(sels, aes(x = MDS1, y = MDS2, col = as.factor(round))) + geom_point() + labs(color = "Round") +
    scale_color_viridis_d(alpha = 0.4) + theme_classic(base_size = 30) + theme(legend.position = c(0.62,
    0.3)) + guides(colour = guide_legend(override.aes = list(size = 10)))
```

```{r RF results 2, eval= TRUE, fig.width= 11, fig.height= 11, echo= FALSE, fig.keep=FALSE, include=FALSE}

vimp <- varImpPlot(urfmod, col = "black", pch = 20, pt.cex = 1.5, n.var = 15, main ="Random Forest classification of cultural evolution models")

vimp <- as.data.frame(vimp)
vimp$params <- rownames(vimp)
vimp <- vimp[order(vimp$MeanDecreaseAccuracy), ]
vimp$params <- as.factor(vimp$params)
vimp$params <- factor(vimp$params, levels = vimp$params[!duplicated(vimp$params)])
vimp <- vimp[(nrow(vimp) - 15):nrow(vimp), ]

ggplot(vimp, aes(x = MeanDecreaseAccuracy, y = params)) + geom_segment(aes(yend = params),
    xend = 0, color = "grey50", size = 1) + geom_point(size = 10, col = viridis(10,
    alpha = 0.6)[2]) + labs(x = "Mean decrease accuracy (RF)", y = "Predictors") +
    theme(legend.key.size = unit(2, "lines")) + scale_color_discrete(name = "Parameter set") +
    scale_fill_discrete(guide = "none") + theme_classic(base_size = 25)
```

PCA
```{r}

pca <- prcomp(x = sels[, c("duration", "meanfreq", "sd", "freq.median", "freq.IQR",
    "time.IQR", "skew", "kurt", "sp.ent", "time.ent", "entropy", "meandom", "mindom",
    "maxdom", "dfrange", "modindx", "meanpeakf")], scale. = TRUE)

Y <- as.data.frame(pca$x[, 1:2])
names(Y) <- c("PC1", "PC2")

sels <- data.frame(sels, Y)

ggplot(sels, aes(x = PC1, y = PC2, col = as.factor(round))) + geom_point() + labs(color = "Round") +
    scale_color_viridis_d(alpha = 0.4) + theme_classic(base_size = 25) + theme(legend.position = c(0.9,
    0.8)) + guides(colour = guide_legend(override.aes = list(size = 10)))
```

t-SNE
```{r, eval = FALSE}

scale_param <- scale(sels[, c("duration", "meanfreq", "sd", "freq.median", "freq.IQR",
    "time.IQR", "skew", "kurt", "sp.ent", "time.ent", "entropy", "meandom", "mindom",
    "maxdom", "dfrange", "modindx", "meanpeakf")])

tsne <- Rtsne(scale_param, dims = 2, perplexity = 30, verbose = FALSE, max_iter = 5000)

saveRDS(tsne, "./data/processed/tsne_on_acoustic_parameters_jun_2021.RDS")
```

```{r}

tsne <- readRDS("./data/processed/tsne_on_acoustic_parameters_jun_2021.RDS")

Y <- as.data.frame(tsne$Y)
names(Y) <- c("TSNE1", "TSNE2")

sels <- data.frame(sels, Y)

ggplot(sels, aes(x = TSNE1, y = TSNE2, col = as.factor(round))) + geom_point() +
    labs(color = "Round") + scale_color_viridis_d(alpha = 0.4) + theme_classic(base_size = 25) +
    theme(legend.position = c(0.955, 0.25)) + guides(colour = guide_legend(override.aes = list(size = 10)))
```

```{r}

sels$treatment <- factor(sels$treatment, levels = c("Control", "Medium Stress", "High Stress"))

ggplot(sels, aes(x = TSNE1, y = TSNE2, col = as.factor(treatment))) + geom_point() +
    labs(color = "Treatment") + scale_color_viridis_d(alpha = 0.4) + theme_classic(base_size = 25) +
    theme(legend.position = c(0.88, 0.2)) + guides(colour = guide_legend(override.aes = list(size = 10)))
```


## Acoustic space by individual (each point) for the 3 dimension reduction methods

- Only individuals with at least 20 calls
- Using rarefaction with n = the minimum sample size across all individuals

```{r, eval = FALSE}
tab <- table(sels$ID)

Y <- sels[sels$ID %in% names(tab[tab > 20]), ]

pca_areas <- rarefact_space_size(X = Y, dimensions = c("PC1", "PC2"), group = "ID", parallel =4, pb = TRUE, type = "density")

rf_mds_areas <- rarefact_space_size(X = Y, dimensions = c("MDS1", "MDS2"), group = "ID", parallel =4, pb = TRUE, type = "density")

tsne_areas <- rarefact_space_size(X = Y, dimensions = c("TSNE1", "TSNE2"), group = "ID", parallel =4, pb = TRUE, type = "density")

areas <- data.frame(pca_areas[,-ncol(pca_areas)], pca.area = pca_areas$mean.size, rf.mds.area = rf_mds_areas$mean.size, tsne.area = tsne_areas$mean.size)

saveRDS(areas, "./data/processed/acoustic_space_area_by_individual_for_each_dimension_reduction_method.RDS")

```

```{r}

areas <- readRDS("./data/processed/acoustic_space_area_by_individual_for_each_dimension_reduction_method.RDS")

ggpairs(areas, columns = which(names(areas) %in% c("pca.area", "rf.mds.area", "tsne.area")),
    columnLabels = c("PCA", "Rand.for. MDS", "t-SNE")) + theme_minimal(base_size = 30)
```


## Individual acoustic space across weeks

- PCA and t-SNE used for dimensionality reduction
- Only weeks with at least 6 calls were included

PCA
```{r, eval = FALSE}

sels$ID.week <- paste(sels$ID, sels$week, sep = "-")

tab <- table(sels$ID.week)

# sort(tab)

Y <- sels[sels$ID.week %in% names(tab)[tab >= 6], ]

# run with rarefaction
areas_by_week_raref <- rarefact_space_size(X = Y, dimensions = c("PC1", "PC2"), group = "ID.week",
    parallel =1, pb = TRUE, type = "density")

# run without rarefaction
areas_by_week <- space_size(X = Y, dimensions = c("PC1", "PC2"), group = "ID.week",
    parallel =1, pb = TRUE, type = "density", extent = 2)

areas_by_week$raref.area <- areas_by_week_raref$mean.size

# add metadata
areas_by_week$ID <- sapply(strsplit(areas_by_week$group, "-"), "[[", 1)

areas_by_week$week <- factor(sapply(strsplit(areas_by_week$group, "-"), "[[", 2),
    levels = 1:5)

areas_by_week$treatment <- sapply(1:nrow(areas_by_week), function(x) metadat$Treatment[metadat$Bird.ID ==
    areas_by_week$ID[x]][1])

areas_by_week$round <- sapply(1:nrow(areas_by_week), function(x) metadat$Round[metadat$Bird.ID ==
    areas_by_week$ID[x]][1])

areas_by_week$round <- paste("Round", areas_by_week$round)

call_count$treatment <- factor(call_count$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

areas_by_week$treatment <- factor(areas_by_week$treatment, levels = c("Control",
    "Medium Stress", "High Stress"))

saveRDS(areas_by_week, "./data/processed/acoustic_space_area_by_individual_and_week.RDS")

```

With rarefaction
```{r}

areas_by_week <- readRDS("./data/processed/acoustic_space_area_by_individual_and_week.RDS")

ggplot(data = areas_by_week, aes(x = week, y = raref.area, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Acoustic space area", x = "Week") +
    theme_classic(base_size = 30) + theme(legend.position = c(0.8, 0.25))
```

With rarefaction and compared to week 1
```{r}

areas_by_week <- readRDS("./data/processed/acoustic_space_area_by_individual_and_week.RDS")

areas_by_week <- do.call(rbind, lapply(unique(areas_by_week$ID), function(x) {

    X <- areas_by_week[areas_by_week$ID == x, ]
    X$raref.area <- X$raref.area - X$raref.area[X$week == min(as.numeric(as.character(X$week)))]
    return(X)
}))

ggplot(data = areas_by_week, aes(x = week, y = raref.area, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Acoustic space area", x = "Week") +
    theme_classic(base_size = 30) + theme(legend.position = c(0.8, 0.25))

```

Without rarefaction
```{r}

ggplot(data = areas_by_week[areas_by_week$week != 5, ], aes(x = week, y = size, group = ID,
    col = treatment)) + geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1,
    end = 0.9) + 
    facet_wrap(~round, ncol = 2) + 
    labs(y = "Acoustic space area", x = "Week") +
    theme_classic(base_size = 30) + theme(legend.position = c(0.8, 0.25))
```

Without rarefaction and compared to week 1
```{r plot acoustic space by individual week with rarefaction compared to week 1, eval = TRUE, fig.width= 7, fig.height= 6}

areas_by_week <- readRDS("./data/processed/acoustic_space_area_by_individual_and_week.RDS")

areas_by_week <- do.call(rbind, lapply(unique(areas_by_week$ID), function(x){
  
  X <- areas_by_week[areas_by_week$ID == x, ]
  X$size <- X$size - X$size[X$week == min(as.numeric(as.character(X$week)))]
  return(X)
}))

ggplot(data = areas_by_week, aes(x = week, y = size, group = ID, col = treatment)) +
    geom_point() +
    geom_line(size = 1.2) +
    scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~ round, ncol = 2) +
    labs(y = "Acoustic space area", x = "Week") +
    theme_classic(base_size = 30) + 
    theme(legend.position = c(0.8, 0.25))

```

Acoustic space area by number of calls per individual and week
```{r}
ggplot(data = areas_by_week, aes(x = n, y = size, col = treatment)) + geom_point() +
    # geom_smooth(size = 1.2, method = 'lm') +
scale_color_viridis_d(begin = 0.1, end = 0.9) + facet_wrap(~round, ncol = 2, scales = "free_x") +
    labs(y = "Acoustic space area", x = "Number of calls (n)") + theme_classic(base_size = 30) +
    theme(legend.position = c(0.8, 0.25))
```

- Acoustic space area by number of calls per individual and week by treatment
- Must have at least 2 calls

```{r}

ggplot(data = areas_by_week, aes(x = n, y = log(size + 10), col = treatment)) + geom_point() +
    geom_smooth(size = 1.2, method = "lm") + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    # facet_wrap(~ round, ncol = 2, scales = 'free_x') +
labs(y = "log(acoustic space area)", x = "Number of calls (n)") + theme_classic(base_size = 30) +
    theme(legend.position = c(0.8, 0.7))
```

## Save acoustic space plots
```{r, eval = FALSE}


plot_space(X = sels, indices = which(sels$ID == "395WBHM"), dimensions = c("TSNE1", "TSNE2"), point.alpha = 0.2, pch = 1)
# 
plot_space(X = sels, indices = which(sels$ID == "395WBHM"), dimensions = c("TSNE1", "TSNE2"), background.indices = which(sels$ID != "395WBHM" & sels$record.group == sels$record.group[sels$ID == "395WBHM"][1]),  point.alpha = 0.2, pch = 1)
```


```{r create plots of acoustic space change over time, eval = FALSE}

# Y <- sels[sels$ID == "395WBHM",]
# Y <- sels[sels$ID %in% c("395WBHM", "394WBHM", "360YGHM", "385YBHM"), ]

# trait_overlap(Y, dimensions = c("TSNE1", "TSNE2"), group = "ID", type = "density", overlap.type = "assymetric")


# X = Y
# dimensions = c("TSNE1", "TSNE2")
# level <- "395WBHM"
# basecex <- 1
# group <- "ID"
# indices <- which(X[, group] == level)

# with points
out <- pblapply(unique(sels$ID), function(x){
 
  tiff(filename = file.path("./images", paste(x, sels$treatment[sels$ID == x][1], "v2.tiff", sep = "-")), res = 100, width = 1200, height = 1200)

   par(mfrow = c(2, 2))

   # W <- sels[sels$ID == x, ]
   
  for(i in 1:4)
    try(plot_space(X = sels, dimensions = c("TSNE1", "TSNE2"), indices = which(sels$ID == x & sels$week == i), background.indices = which(sels$ID != x & sels$week == i & sels$record.group == sels$record.group[sels$ID == x][1]), title = paste(x, "week", i), basecex = 1, labels = c(x, "group")), silent = TRUE)
  
    dev.off()
  })


```


## TSNE
```{r, eval = FALSE}

sels$ID.week <- paste(sels$ID, sels$week, sep = "-")

tab <- table(sels$ID.week)

# sort(tab)

Y <- sels[sels$ID.week %in% names(tab)[tab >= 6], ]

# run with rarefaction
areas_by_week_raref <- rarefact_space_size(X = Y, dimensions = c("TSNE1", "TSNE2"),
    group = "ID.week", parallel =1, pb = TRUE, type = "density")

# run without rarefaction
areas_by_week <- space_size(X = Y, dimensions = c("TSNE1", "TSNE2"), group = "ID.week",
    parallel =4, pb = TRUE,
    type = "density")

areas_by_week$raref.area <- areas_by_week_raref$mean.size

# add metadata
areas_by_week$ID <- sapply(strsplit(areas_by_week$group, "-"), "[[", 1)

areas_by_week$week <- factor(sapply(strsplit(areas_by_week$group, "-"), "[[", 2),
    levels = 1:5)

areas_by_week$treatment <- sapply(1:nrow(areas_by_week), function(x) metadat$Treatment[metadat$Bird.ID ==
    areas_by_week$ID[x]][1])

areas_by_week$round <- sapply(1:nrow(areas_by_week), function(x) metadat$Round[metadat$Bird.ID ==
    areas_by_week$ID[x]][1])

areas_by_week$round <- paste("Round", areas_by_week$round)

call_count$treatment <- factor(call_count$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

areas_by_week$treatment <- factor(areas_by_week$treatment, levels = c("Control",
    "Medium Stress", "High Stress"))

saveRDS(areas_by_week, "./data/processed/acoustic_space_area_by_individual_and_week_TSNE.RDS")

```

With rarefaction
```{r}

areas_by_week <- readRDS("./data/processed/acoustic_space_area_by_individual_and_week_TSNE.RDS")

ggplot(data = areas_by_week, aes(x = week, y = raref.area, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Acoustic space area", x = "Week") +
    theme_classic(base_size = 30) + theme(legend.position = c(0.8, 0.25))
```


With rarefaction and compared to week 1
```{r}

areas_by_week <- readRDS("./data/processed/acoustic_space_area_by_individual_and_week_TSNE.RDS")

areas_by_week <- do.call(rbind, lapply(unique(areas_by_week$ID), function(x) {

    X <- areas_by_week[areas_by_week$ID == x, ]
    X$raref.area <- X$raref.area - X$raref.area[X$week == min(as.numeric(as.character(X$week)))]
    return(X)
}))

ggplot(data = areas_by_week, aes(x = week, y = raref.area, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Acoustic space area", x = "Week") +
    theme_classic(base_size = 30) + theme(legend.position = c(0.8, 0.25))
```

Without rarefaction
```{r}

ggplot(data = areas_by_week[areas_by_week$week != 5, ], aes(x = week, y = size, group = ID,
    col = treatment)) + geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1,
    end = 0.9) + facet_wrap(~round, ncol = 2) + labs(y = "Acoustic space area", x = "Week") +
    theme_classic(base_size = 30) + theme(legend.position = c(0.8, 0.25))
```

Without rarefaction and compared to week 1
```{r plot acoustic space by individual week and compared to week 1 , eval = TRUE, fig.width= 7, fig.height= 6}

areas_by_week <- do.call(rbind, lapply(unique(areas_by_week$ID), function(x){
  
  X <- areas_by_week[areas_by_week$ID == x, ]
  X$size <- X$size - X$size[X$week == min(as.numeric(as.character(X$week)))]
  return(X)
}))

ggplot(data = areas_by_week, aes(x = week, y = size, group = ID, col = treatment)) +
    geom_point() +
    geom_line(size = 1.2) +
    scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~ round, ncol = 2) +
    labs(y = "Acoustic space area", x = "Week") +
    theme_classic(base_size = 30) + 
    theme(legend.position = c(0.8, 0.25))

```

Acoustic space area by number of calls per individual and week
```{r}

ggplot(data = areas_by_week, aes(x = n, y = size, col = treatment)) + geom_point() +
    # geom_smooth(size = 1.2, method = 'lm') +
scale_color_viridis_d(begin = 0.1, end = 0.9) + facet_wrap(~round, ncol = 2, scales = "free_x") +
    labs(y = "Acoustic space area", x = "Number of calls (n)") + theme_classic(base_size = 30) +
    theme(legend.position = c(0.8, 0.25))
```


- Acoustic space area by number of calls per individual and week by treatment
- Must have at least 2 calls

```{r}
ggplot(data = areas_by_week, aes(x = n, y = log(size + 10), col = treatment)) + geom_point() +
    geom_smooth(size = 1.2, method = "lm") + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    # facet_wrap(~ round, ncol = 2, scales = 'free_x') +
labs(y = "log(acoustic space area)", x = "Number of calls (n)") + theme_classic(base_size = 30) +
    theme(legend.position = c(0.8, 0.7))
```

## Acoustic space overlap

- 2 methods: pairwise distance between observations and kernel density overlap


## Individual overlap to its own group

### PCA

```{r overlap to group by week, eval = FALSE}

sels$ID.week <- paste(sels$ID, sels$week, sep = "-")
tab <- table(sels$ID)
Y <- sels[sels$ID %in% names(tab)[tab >= 2], ]

group_ovlp_l <- lapply(unique(Y$ID.week), function(x){
  
  # group data
  X <- Y[Y$record.group == Y$record.group[Y$ID.week == x][1] & Y$week == Y$week[Y$ID.week == x][1], ]

  # label all other individuals as group
  X$ID2 <- ifelse(X$ID.week == x, "focal", "group")
  
# run with density
  ovlp <- if (min(table(X$ID2)) > 4)
  rarefact_space_similarity(X = X, dimensions = c("PC1", "PC2"), group = "ID2", parallel = 1, pb = FALSE, outliers = 0.95, type = "mean.density.overlap") else matrix(rep(NA, 3), nrow = 1)
  
  dsts <- if (min(table(X$ID2)) > 1) 
    rarefact_space_similarity(X = X, dimensions = c("PC1", "PC2"), group = "ID2", parallel = 1, pb = FALSE, outliers = 0.95, type = "distance") else matrix(rep(NA, 3), nrow = 1)

  out <- data.frame(ID = Y$ID[Y$ID.week == x][1], group = Y$record.group[Y$ID.week == x][1], week = Y$week[Y$ID.week == x][1], overlap.to.group = ovlp[1, 3],  distance.to.group = dsts[1, 3], treatment = Y$treatment[Y$ID.week == x][1], round = Y$round[Y$ID.week == x][1])
  
  return(out)
  
  })

group_ovlp <- do.call(rbind, group_ovlp_l)

saveRDS(group_ovlp, "./data/processed/acoustic_space_density_overlap_to_group_by_week.RDS")

```


```{r plot overlap to group by week, fig.width = 16, fig.height = 10, eval = TRUE}

group_ovlp <- readRDS("./data/processed/acoustic_space_density_overlap_to_group_by_week.RDS")


group_ovlp <- do.call(rbind, lapply(unique(group_ovlp$ID), function(x){
  
  X <- group_ovlp[group_ovlp$ID == x, ]
  X$overlap.to.group <- X$overlap.to.group - X$overlap.to.group[X$week == min(as.numeric(as.character(X$week)))]
   X$distance.to.group <- X$distance.to.group - X$distance.to.group[X$week == min(as.numeric(as.character(X$week)))]
  return(X)
}))


group_ovlp$treatment <- factor(group_ovlp$treatment, levels = c("Control", "Medium Stress", "High Stress"))

ggplot(data = group_ovlp, aes(x = week, y = overlap.to.group, group = ID, col = treatment)) +
    geom_point() +
    geom_line(size = 1.2) +
    scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~ round, ncol = 2) +
    labs(y = "Individual overlap to group acoustic space", x = "Week") +
    theme_classic(base_size = 30) + 
    theme(legend.position = c(0.8, 0.25))

ggplot(data = group_ovlp, aes(x = week, y = overlap.to.group, group = ID, col = treatment)) +
    geom_point() +
    geom_line(size = 1.2) +
    scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~ round, ncol = 2) +
    labs(y = "Individual distance to group acoustic space", x = "Week") +
    theme_classic(base_size = 30) + 
    theme(legend.position = c(0.8, 0.25))


```

```{r acoustic space overlap by id week, eval = FALSE}

sels$ID.week <- paste(sels$ID, sels$week, sep = "-")

tab <- table(sels$ID.week)

Y <- sels[sels$ID.week %in% names(tab)[tab >= 6], ]

# run with rarefaction
overlap_by_week <- rarefact_space_similarity(X = Y, dimensions = c("PC1", "PC2"), group = "ID.week", parallel = 1, pb = TRUE, outliers = 0.95, type = "mean.density.overlap") 

saveRDS(overlap_by_week, "./data/processed/acoustic_space_overlap_by_individual_and_week.RDS")
```

### TSNE
```{r, eval = FALSE}

sels$ID.week <- paste(sels$ID, sels$week, sep = "-")
tab <- table(sels$ID)
Y <- sels[sels$ID %in% names(tab)[tab >= 6], ]

group_ovlp_l <- lapply(unique(Y$ID.week), function(x) {

    # group data
    X <- Y[Y$record.group == Y$record.group[Y$ID.week == x][1] & Y$week == Y$week[Y$ID.week == x][1], ]

    # label all other individuals as group
    X$ID2 <- ifelse(X$ID.week == x, "focal", "group")

    # run with density
    ovlp <- if (min(table(X$ID2)) >= 6)
        rarefact_space_similarity(X = X, dimensions = c("TSNE1", "TSNE2"), group = "ID2",
            parallel = 1, pb = FALSE, type = "mean.density.overlap")[, 1:3] else matrix(rep(NA, 3), nrow = 1)

    dsts <- if (min(table(X$ID2)) >= 2)
        rarefact_space_similarity(X = X, dimensions = c("TSNE1", "TSNE2"), group = "ID2",
            parallel = 1, pb = FALSE, type = "distance")[, 1:3]  else matrix(rep(NA, 3), nrow = 1)

    out <- data.frame(ID = X$ID[X$ID.week == x][1], group = X$record.group[X$ID.week ==
        x][1], week = X$week[X$ID.week == x][1], overlap.to.group = ovlp[1, 3], distance.to.group = dsts[1, 3], treatment = X$treatment[X$ID.week == x][1], round = X$round[X$ID.week ==
        x][1])

    return(out)

})

group_ovlp <- do.call(rbind, group_ovlp_l)


saveRDS(group_ovlp, "./data/processed/acoustic_space_density_overlap_to_group_by_week_TSNE.RDS")

```

```{r}

group_ovlp <- readRDS("./data/processed/acoustic_space_density_overlap_to_group_by_week_TSNE.RDS")


# comparing to week 1 group_ovlp <- do.call(rbind,
# lapply(unique(group_ovlp$ID), function(x){ X <- group_ovlp[group_ovlp$ID ==
# x, ] X$overlap.to.group <- X$overlap.to.group / X$overlap.to.group[X$week ==
# min(as.numeric(as.character(X$week)))] X$distance.to.group <-
# X$distance.to.group - X$distance.to.group[X$week ==
# min(as.numeric(as.character(X$week)))] return(X) }))


group_ovlp$treatment <- factor(group_ovlp$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

ggplot(data = group_ovlp, aes(x = week, y = overlap.to.group, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Individual overlap to group acoustic space",
    x = "Week") + theme_classic(base_size = 30) + theme(legend.position = c(0.8,
    0.25))
```

## Change in overlap with self over time

### PCA

```{r, eval = FALSE}

tab <- table(sels$ID)
Y <- sels[sels$ID %in% names(tab)[tab >= 6], ]

indiv_ovlp_l <- lapply(unique(Y$ID), function(x) {


    # group data
    X <- Y[Y$ID == x, ]
    tab_week <- table(X$week)
    X <- X[X$week %in% names(tab_week)[tab_week >= 6], ]

    if (any(X$week == 1)){
    # run with density
    ovlp <- try(rarefact_space_similarity(X = X, dimensions = c("PC1", "PC2"), group = "week",
            parallel = 1, pb = FALSE, type = "mean.density.overlap"), silent = TRUE)

    dsts <- try(rarefact_space_similarity(X = X, dimensions = c("PC1", "PC2"), group = "week",
            parallel = 1, pb = FALSE, type = "distance"), silent = TRUE)

    out <- data.frame(ID = x, group = X$record.group[X$ID == x][1], week = if(is(ovlp, "try-error")) NA else ovlp$group.2[ovlp$group.1 == 1],
        overlap.to.first.week = if(is(ovlp, "try-error")) NA else ovlp$mean.overlap[ovlp$group.1 == 1], distance.to.first.week = if(is(dsts, "try-error")) NA else dsts$mean.distance[dsts$group.1 == 1], treatment = X$treatment[X$ID ==
            x][1], round = X$round[X$ID == x][1])
} else
  out <- data.frame(ID = x, group = X$record.group[X$ID == x][1], week = NA,
        overlap.to.first.week = NA, distance.to.first.week = NA, treatment = X$treatment[X$ID ==
            x][1], round = X$round[X$ID == x][1])
    return(out)

})

indiv_ovlp <- do.call(rbind, indiv_ovlp_l)

saveRDS(indiv_ovlp, "./data/processed/acoustic_space_density_overlap_to_first_week_by_individual.RDS")
```

```{r}

indiv_ovlp <- readRDS("./data/processed/acoustic_space_density_overlap_to_first_week_by_individual.RDS")

indiv_ovlp$treatment <- factor(indiv_ovlp$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))
indiv_ovlp <- indiv_ovlp[!is.na(indiv_ovlp$group), ]

ggplot(data = indiv_ovlp, aes(x = week, y = overlap.to.first.week, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Individual overlap to acoustic space from first week",
    x = "Week") + theme_classic(base_size = 30) + theme(legend.position = c(0.8,
    0.25))
```

```{r}

ggplot(data = indiv_ovlp, aes(x = week, y = distance.to.first.week, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Individual distance to acoustic space from first week",
    x = "Week") + theme_classic(base_size = 30) + theme(legend.position = c(0.8,
    0.25))
```

```{r, eval = FALSE}
agg_dist <- aggregate(distance.to.first.week ~ week + treatment, indiv_ovlp, mean)
agg_dist$se <- aggregate(distance.to.first.week ~ week + treatment, indiv_ovlp, standard_error)[,
    3]
agg_dist$Week <- 1:4

# ggplot(data = agg_dist, aes(x = Week, y = distance.to.first.week, fill =
# treatment)) + geom_bar(stat = 'identity') +
# geom_errorbar(aes(ymin=distance.to.first.week - se, ymax =
# distance.to.first.week + se), width=.1) + # geom_line(size = 1.2) +
# scale_fill_viridis_d(begin = 0.1, end = 0.9) + facet_wrap(~ treatment, ncol =
# 3, scale = 'fixed') + labs(y = 'Distance to self first week', x = 'Week') +
# theme_classic(base_size = 30) + # scale_x_discrete( labels = c(1:4)) +
# theme(legend.position = 'none')


agg_ovlp <- aggregate(overlap.to.first.week ~ week + treatment, indiv_ovlp, mean)
agg_ovlp$se <- aggregate(overlap.to.first.week ~ week + treatment, indiv_ovlp, standard_error)[,
    3]
agg_ovlp$Week <- 1:4

# ggplot(data = agg_ovlp, aes(x = Week, y = overlap.to.first.week, fill =
# treatment)) + geom_bar(stat = 'identity') +
# geom_errorbar(aes(ymin=overlap.to.first.week - se, ymax =
# overlap.to.first.week + se), width=.1) + # geom_line(size = 1.2) +
# scale_fill_viridis_d(begin = 0.1, end = 0.9) + facet_wrap(~ treatment, ncol =
# 3, scale = 'fixed') + labs(y = 'Overlap to \nself first week', x = 'Week') +
# theme_classic(base_size = 30) + # scale_x_discrete( labels = c(1:4)) +
# theme(legend.position = 'none')

```

## TSNE

```{r, eval= FALSE}

tab <- table(sels$ID)
Y <- sels[sels$ID %in% names(tab)[tab >= 2], ]

indiv_ovlp_l <- lapply(unique(Y$ID), function(x) {


    # group data
    X <- Y[Y$ID == x, ]
    tab_week <- table(X$week)
    X <- X[X$week %in% names(tab_week)[tab_week >= 6], ]

    if (any(X$week == 1)){
    # run with density
    ovlp <- try(rarefact_space_similarity(X = X, dimensions = c("TSNE1", "TSNE2"), group = "week",
            parallel = 1, pb = FALSE, type = "mean.density.overlap"), silent = TRUE)

    dsts <- try(rarefact_space_similarity(X = X, dimensions = c("TSNE1", "TSNE2"), group = "week",
            parallel = 1, pb = FALSE, type = "distance"), silent = TRUE)

    out <- data.frame(ID = x, group = X$record.group[X$ID == x][1], week = if(is(ovlp, "try-error")) NA else ovlp$group.2[ovlp$group.1 == 1],
        overlap.to.first.week = if(is(ovlp, "try-error")) NA else ovlp$mean.overlap[ovlp$group.1 == 1], distance.to.first.week = if(is(dsts, "try-error")) NA else dsts$mean.distance[dsts$group.1 == 1], treatment = X$treatment[X$ID ==
            x][1], round = X$round[X$ID == x][1])
} else
  out <- data.frame(ID = x, group = X$record.group[X$ID == x][1], week = NA,
        overlap.to.first.week = NA, distance.to.first.week = NA, treatment = X$treatment[X$ID ==
            x][1], round = X$round[X$ID == x][1])
    return(out)

})

indiv_ovlp <- do.call(rbind, indiv_ovlp_l)

saveRDS(indiv_ovlp, "./data/processed/acoustic_space_density_overlap_to_first_week_by_individual_TSNE.RDS")

```

```{r}

indiv_ovlp <- readRDS("./data/processed/acoustic_space_density_overlap_to_first_week_by_individual_TSNE.RDS")

indiv_ovlp$treatment <- factor(indiv_ovlp$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))
indiv_ovlp <- indiv_ovlp[!is.na(indiv_ovlp$group), ]

ggplot(data = indiv_ovlp, aes(x = week, y = overlap.to.first.week, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Individual overlap to acoustic space from first week",
    x = "Week") + theme_classic(base_size = 30) + theme(legend.position = c(0.8,
    0.25))
```

```{r}

ggplot(data = indiv_ovlp, aes(x = week, y = distance.to.first.week, group = ID, col = treatment)) +
    geom_point() + geom_line(size = 1.2) + scale_color_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~round, ncol = 2) + labs(y = "Individual distance to acoustic space from first week",
    x = "Week") + theme_classic(base_size = 30) + theme(legend.position = c(0.8,
    0.25))
```

```{r, eval=FALSE}

agg_dist <- aggregate(distance.to.first.week ~ week + treatment, indiv_ovlp, mean)
agg_dist$se <- aggregate(distance.to.first.week ~ week + treatment, indiv_ovlp, standard_error)[,
    3]
# agg_stress$Week <- 1:4


# ggplot(data = agg_dist, aes(x = week, y = distance.to.first.week, fill =
# treatment)) + geom_bar(stat = 'identity') +
# geom_errorbar(aes(ymin=distance.to.first.week - se, ymax =
# distance.to.first.week + se), width=.1) + # geom_line(size = 1.2) +
# scale_fill_viridis_d(begin = 0.1, end = 0.9) + facet_wrap(~ treatment, ncol =
# 3, scale = 'fixed') + labs(y = 'Distance to first week', x = 'Week') +
# theme_classic(base_size = 30) + # scale_x_discrete( labels = c(1:4)) +
# theme(legend.position = 'none')
```

# Statistical analyses

- on t-SNE dimensions
- predictors were mean-centered
- link functions: binomial distribution for overlap and gaussian for area and call count
- cort.stress and cort.baseline were dropped as they are highly correlated to stress response
- Not a lot of data makes having many predictors complicated
- No random factor (only 1 row per individual)
- No p values printed. Look at whether credibility intervals (l-95% CI & u-95% CI) include 0 to assess statistical significance

## Overlap to self (week 1) as response

overlap.to.first.week ~ treatment + stress.response

```{r}

sels$ID.week <- paste(sels$ID, sels$week, sep = "-")
indiv_ovlp$ID.week <- paste(indiv_ovlp$ID, indiv_ovlp$week, sep = "-")

# addd stress parameters
indiv_ovlp$cort.baseline <- sapply(indiv_ovlp$ID.week, function(x) sels$cort.baseline[sels$ID.week ==
    x][1])
indiv_ovlp$cort.stress <- sapply(indiv_ovlp$ID.week, function(x) sels$cort.stress[sels$ID.week ==
    x][1])
indiv_ovlp$breath.count <- sapply(indiv_ovlp$ID.week, function(x) sels$breath.count[sels$ID.week ==
    x][1])
indiv_ovlp$stress.response <- indiv_ovlp$cort.stress - indiv_ovlp$cort.baseline

# mean centering
indiv_ovlp$cort.baseline <- mean(indiv_ovlp$cort.baseline, na.rm = TRUE) - indiv_ovlp$cort.baseline
indiv_ovlp$cort.stress <- mean(indiv_ovlp$cort.stress, na.rm = TRUE) - indiv_ovlp$cort.stress
indiv_ovlp$breath.count <- mean(indiv_ovlp$breath.count, na.rm = TRUE) - indiv_ovlp$breath.count
indiv_ovlp$stress.response <- mean(indiv_ovlp$stress.response, na.rm = TRUE) - indiv_ovlp$stress.response


# only individuals present in week 1
# indiv_ovlp <- indiv_ovlp[indiv_ovlp$ID %in% indiv_ovlp$ID[indiv_ovlp$week == 1],
#     ]

# indiv_ovlp <- indiv_ovlp[complete.cases(indiv_ovlp), ]

indiv_ovlp$overlap.to.first.week[indiv_ovlp$overlap.to.first.week == 0] <- 1e-04
indiv_ovlp$overlap.to.first.week[indiv_ovlp$overlap.to.first.week == 1] <- 0.9999
```

week 2:
```{r, eval = FALSE}
## week 2

overlap_week_2 <- brm(iter = 5000, silent = 2, overlap.to.first.week ~ treatment +
    stress.response, data = indiv_ovlp[indiv_ovlp$week == 2, ], family = Beta(),
    control = list(adapt_delta = 0.9), chains = 1)

saveRDS(overlap_week_2, "./data/processed/brms_model_overlap_week_2.RDS")
```

```{r, results = 'asis'}
overlap_week_2 <- readRDS("./data/processed/brms_model_overlap_week_2.RDS")

summary_brm_model(overlap_week_2)

```

week 4:
```{r, eval = FALSE}
## week 4
overlap_week_4 <- brm(iter = 5000, silent = 2, overlap.to.first.week ~ treatment +
    stress.response, data = indiv_ovlp[indiv_ovlp$week == 4, ], family = Beta(),
    control = list(adapt_delta = 0.9, max_treedepth = 12), chains = 1)

saveRDS(overlap_week_4, "./data/processed/brms_model_overlap_week_4.RDS")

```

```{r, results = 'asis'}
overlap_week_4 <- readRDS("./data/processed/brms_model_overlap_week_4.RDS")

summary_brm_model(overlap_week_4)

```

## Acoustic space change (compare to week 1)

area ~ treatment + stress.response
```{r}

areas_by_week$ID.week <- paste(areas_by_week$ID, areas_by_week$week, sep = "-")


# addd stress parameters
areas_by_week$cort.baseline <- sapply(areas_by_week$ID.week, function(x) sels$cort.baseline[sels$ID.week ==
    x][1])
areas_by_week$cort.stress <- sapply(areas_by_week$ID.week, function(x) sels$cort.stress[sels$ID.week ==
    x][1])
areas_by_week$breath.count <- sapply(areas_by_week$ID.week, function(x) sels$breath.count[sels$ID.week ==
    x][1])
areas_by_week$stress.response <- areas_by_week$cort.stress - areas_by_week$cort.baseline

# mean centering
areas_by_week$cort.baseline <- mean(areas_by_week$cort.baseline, na.rm = TRUE) -
    areas_by_week$cort.baseline
areas_by_week$cort.stress <- mean(areas_by_week$cort.stress, na.rm = TRUE) - areas_by_week$cort.stress
areas_by_week$breath.count <- mean(areas_by_week$breath.count, na.rm = TRUE) - areas_by_week$breath.count
areas_by_week$stress.response <- mean(areas_by_week$stress.response, na.rm = TRUE) -
    areas_by_week$stress.response


# only individuals present in week 1
# areas_by_week <- areas_by_week[areas_by_week$ID %in% areas_by_week$ID[areas_by_week$week ==
#     1], ]


# areas_by_week <- areas_by_week[complete.cases(areas_by_week), ]
```

week 2:
```{r, eval = FALSE}

## week 2
area_week_2 <- brm(iter = 5000, silent = 2, size ~ treatment + stress.response, data = areas_by_week[areas_by_week$week ==
    2, ], control = list(adapt_delta = 0.9), chains = 1)

saveRDS(area_week_2, "./data/processed/brms_model_area_week_2.RDS")
```

```{r, results = 'asis'}

area_week_2 <- readRDS("./data/processed/brms_model_area_week_2.RDS")

summary_brm_model(area_week_2)
```

week 4:
```{r, eval = FALSE}

## week 4
area_week_4 <- brm(iter = 5000, silent = 2, size ~ treatment + stress.response, data = areas_by_week[areas_by_week$week ==
    4, ], control = list(adapt_delta = 0.9), chains = 1)

saveRDS(area_week_4, "./data/processed/brms_model_area_week_4.RDS")
```

```{r, results = 'asis'}

area_week_4 <- readRDS("./data/processed/brms_model_area_week_4.RDS")

summary_brm_model(area_week_4)
```

## Call count

week 2:
```{r, eval = FALSE}

## week 2
count_week_2 <- brm(iter = 5000, silent = 2, selec ~ treatment + stress.response,
    data = call_count[call_count$week == 2, ], control = list(adapt_delta = 0.9),
    chains = 1)

saveRDS(count_week_2, "./data/processed/brms_model_count_week_2.RDS")
```


```{r, results = 'asis'}
count_week_2 <- readRDS("./data/processed/brms_model_count_week_2.RDS")

summary_brm_model(count_week_2)
```

week 4:
```{r, eval = FALSE}

## week 4
count_week_4 <- brm(iter = 5000, silent = 2, selec ~ treatment + stress.response,
    data = call_count[call_count$week == 4, ], control = list(adapt_delta = 0.9),
    chains = 1)

saveRDS(count_week_4, "./data/processed/brms_model_count_week_4.RDS")
```


```{r, results = 'asis'}
count_week_4 <- readRDS("./data/processed/brms_model_count_week_4.RDS")

summary_brm_model(count_week_4)
```
&nbsp;

<div class="alert alert-info">

## Takeaways

- Stress has an effect on number of calls: high-stress individuals produce more calls than low-stress individuals in week 2
- Stress response has a positive effect on the overlap to week 1 (overlap to itself)

</div>

&nbsp;

---

# Proposed Models for Stress and Learning Pilot Data based on 9/28/21 discussion

## Model set 1: effects of treatment

Predicted variables: - Physiology: Baseline CORT, stress response CORT (stress), difference baseline-stress response CORT (stress response), weight, breath rate - Learning: number of calls, total acoustic area, distance moved from week 1, overlap to self week 1, overlap self to group

General form: - Predicted ~ treatment + week + ind(rand) - Predicted ~ treatment + week + treat * week + ind(rand) - Predicted ~ round + week [to check for effect of round]

Note: Use week 1 as baseline, comparing weeks 2, 3, 4

```{r}
agg_dat <- aggregate(selec ~ ID + week, data = sels, length)

# compare to week 1 agg_dat$call.count <- sapply(1:nrow(agg_dat), function(x) {
# baseline <- agg_dat$selec[agg_dat$week == 1 & agg_dat$ID == agg_dat$ID[x]] if
# (length(baseline) > 0) change <- agg_dat$selec[x] - baseline else change <-
# agg_dat$selec[x] return(change) } )

# without comparing to week 1
agg_dat$call.count <- sapply(1:nrow(agg_dat), function(x) agg_dat$selec[x])

agg_dat$selec <- NULL

agg_dat$baseline.CORT <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$cort.baseline[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$cort.baseline[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})

agg_dat$stress.response <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$stress.response[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$stress.response[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})


agg_dat$stress.CORT <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$cort.stress[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$cort.stress[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})

agg_dat$weight <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$weight[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$weight[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})

agg_dat$breath.rate <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$breath.count[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$breath.count[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})

agg_dat$acoustic.area <- sapply(1:nrow(agg_dat), function(x) {

    area <- areas_by_week$raref.area[areas_by_week$ID == agg_dat$ID[x] & areas_by_week$week ==
        agg_dat$week[x]]

    if (length(area) < 1)
        area <- NA

    return(area)
})


agg_dat$acoustic.distance <- sapply(1:nrow(agg_dat), function(x) {

    distance <- indiv_ovlp$distance.to.first.week[indiv_ovlp$ID == agg_dat$ID[x] &
        indiv_ovlp$week == agg_dat$week[x]]

    if (length(distance) < 1)
        distance <- NA

    return(distance)
})

agg_dat$acoustic.overlap <- sapply(1:nrow(agg_dat), function(x) {

    overlap <- indiv_ovlp$overlap.to.first.week[indiv_ovlp$ID == agg_dat$ID[x] &
        indiv_ovlp$week == agg_dat$week[x]]

    if (length(overlap) < 1)
        overlap <- NA

    return(overlap)
})

agg_dat$acoustic.overlap.to.group <- sapply(1:nrow(agg_dat), function(x) {

    overlap <- group_ovlp$overlap.to.group[group_ovlp$ID == agg_dat$ID[x] & group_ovlp$week ==
        agg_dat$week[x]]

    if (length(overlap) < 1)
        overlap <- NA

    return(overlap)
})


agg_dat$treatment <- sapply(1:nrow(agg_dat), function(x) unique(sels$treatment[sels$ID ==
    agg_dat$ID[x]]))

agg_dat$round <- sapply(1:nrow(agg_dat), function(x) unique(sels$round[sels$ID ==
    agg_dat$ID[x]]))

# remove week 1
agg_dat <- agg_dat[agg_dat$week != 1, ]


responses <- setdiff(names(agg_dat), c("ID", "week", "treatment", "round"))

predictors <- c("~ treatment + week + (1|ID)", "~ treatment * week + (1|ID)", "~ round + week + (1|ID)")

formulas <- expand.grid(responses = responses, predictors = predictors, stringsAsFactors = FALSE)
```

```{r, eval = FALSE}
vars_to_scale <- names(agg_dat)[sapply(agg_dat, is.numeric)]
vars_to_scale <- vars_to_scale[!vars_to_scale %in% c("week", "round")]

for (i in vars_to_scale) agg_dat[, vars_to_scale] <- scale(agg_dat[, vars_to_scale])

treatment_models <- lapply(1:nrow(formulas), function(x) {

    sub_dat <- agg_dat[!is.na(agg_dat[names(agg_dat) == formulas$responses[x]]),
        ]
    sub_dat

    mod <- try(brm(formula = paste(formulas$responses[x], formulas$predictors[x]),
        iter = 5000, silent = 2, data = sub_dat, control = list(adapt_delta = 0.9),
        chains = 2), silent = TRUE)
    return(mod)
})


names(treatment_models) <- paste(formulas$responses, formulas$predictors)

saveRDS(treatment_models, "./data/processed/treatment_models.RDS")

agg_dat$week <- as.factor(agg_dat$week)

treatment_models_week_factor <- lapply(1:nrow(formulas), function(x) {

    sub_dat <- agg_dat[!is.na(agg_dat[names(agg_dat) == formulas$responses[x]]),
        ]

    mod <- try(brm(formula = paste(formulas$responses[x], formulas$predictors[x]),
        iter = 5000, silent = 2, data = sub_dat, control = list(adapt_delta = 0.9),
        chains = 2), silent = TRUE)
    return(mod)
})

names(treatment_models_week_factor) <- paste(formulas$responses, formulas$predictors)

saveRDS(treatment_models_week_factor, "./data/processed/treatment_models_week_factor.RDS")

```

### week as continuous
```{r, results = 'asis'}

treatment_models <- readRDS("./data/processed/treatment_models.RDS")



for (x in treatment_models) {
  summary_brm_model(x)
  }
```

&nbsp;

<div class="alert alert-info">

## Takeaways

- No significant nor marginal effects 
</div>

&nbsp;

## Model set 2: individual stress and effects on learning

General form: - Learning variables ~ baseline CORT [Week 2 immediate stress and learning, week 3 chronic stress and learn]


```{r}
agg_dat <- agg_dat[agg_dat$week != "4", ]

agg_dat$week <- as.factor(agg_dat$week)


responses <- c("call.count", "acoustic.area", "acoustic.distance", "acoustic.overlap",
    "acoustic.overlap.to.group")

predictors <- c("~ baseline.CORT + week + (1|ID)", "~ stress.response + week + (1|ID)")

formulas <- expand.grid(responses = responses, predictors = predictors, stringsAsFactors = FALSE)
```

```{r, eval = FALSE}
treatment_models <- lapply(1:nrow(formulas), function(x) {

    sub_dat <- agg_dat[!is.na(agg_dat[names(agg_dat) == formulas$responses[x]]),
        ]

    mod <- try(brm(formula = paste(formulas$responses[x], formulas$predictors[x]),
        iter = 5000, silent = 2, data = sub_dat, control = list(adapt_delta = 0.9),
        chains = 1), silent = TRUE)
    return(mod)
})


names(treatment_models) <- paste(formulas$responses, formulas$predictors)

saveRDS(treatment_models, "./data/processed/stress_on_learning_models.RDS")

```

```{r, results = 'asis'}
treatment_models <- readRDS("./data/processed/stress_on_learning_models.RDS")



for (x in treatment_models) {
  summary_brm_model(x)
  }

```

&nbsp;

<div class="alert alert-info">

## Takeaways

- No significant effects

</div>

&nbsp;

## Model set 3: individual stress and effects on learning on week 2 and 3 independently

Week 2 immediate stress and learning, week 3 chronic stress and learn

General form: - Learning variables ~ baseline CORT - Learning variables ~ difference baseline-stress CORT

Week 2
```{r, eval = FALSE}

agg_dat_w2 <- agg_dat[agg_dat$week == "2", ]

responses <- c("call.count", "acoustic.area", "acoustic.distance", "acoustic.overlap",
    "acoustic.overlap.to.group")

predictors <- c("~ baseline.CORT + (1|ID)", "~ stress.response + (1|ID)")

formulas <- expand.grid(responses = responses, predictors = predictors, stringsAsFactors = FALSE)

treatment_models <- lapply(1:nrow(formulas), function(x) {

    sub_dat <- agg_dat_w2[!is.na(agg_dat_w2[names(agg_dat_w2) == formulas$responses[x]]),
        ]

    mod <- try(brm(formula = paste(formulas$responses[x], formulas$predictors[x]),
        iter = 5000, silent = 2, data = sub_dat, control = list(adapt_delta = 0.9),
        chains = 1), silent = TRUE)
    return(mod)
})


names(treatment_models) <- paste(formulas$responses, formulas$predictors)

saveRDS(treatment_models, "./data/processed/stress_on_learning_models_week_2.RDS")
```

```{r, results = 'asis'}

treatment_models <- readRDS("./data/processed/stress_on_learning_models_week_2.RDS")

for (x in treatment_models) {
  summary_brm_model(x)
  }
```

Week 3
```{r, eval = FALSE}

agg_dat_w3 <- agg_dat[agg_dat$week == "3", ]

responses <- c("call.count", "acoustic.area", "acoustic.distance", "acoustic.overlap",
    "acoustic.overlap.to.group")

predictors <- c("~ baseline.CORT + (1|ID)", "~ stress.response + (1|ID)")

formulas <- expand.grid(responses = responses, predictors = predictors, stringsAsFactors = FALSE)

treatment_models <- lapply(1:nrow(formulas), function(x) {

    sub_dat <- agg_dat_w3[!is.na(agg_dat_w3[names(agg_dat_w3) == formulas$responses[x]]),
        ]

    mod <- try(brm(formula = paste(formulas$responses[x], formulas$predictors[x]),
        iter = 5000, silent = 2, data = sub_dat, control = list(adapt_delta = 0.9),
        chains = 1), silent = TRUE)
    return(mod)
})


names(treatment_models) <- paste(formulas$responses, formulas$predictors)

saveRDS(treatment_models, "./data/processed/stress_on_learning_models_week_3.RDS")
```

```{r, results = 'asis'}

treatment_models <- readRDS("./data/processed/stress_on_learning_models_week_3.RDS")

for (x in treatment_models) {
  summary_brm_model(x)
  }
```


&nbsp;

<div class="alert alert-info">

## Takeaways

- No significant nor marginal effects

</div>

&nbsp;

---

<font size="4">Session information</font>

```{r session info, echo=F, eval = TRUE}

sessionInfo()

```