---
title: Variation in vocal behavior under varying stress levels
subtitle: Budgie INBRE stress and contact calls
author: <a href="http://marceloarayasalas.weebly.com/">Marcelo Araya-Salas, PhD</a> & <a href="https://wrightbehaviorlab.org/">Timothy Wright, PhD</a>
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_depth: 3
    css: rmd.css
    df_print: kable
    toc_float:
      collapsed: yes
      smooth_scroll: yes
fontsize: 12pt 
editor_options: 
  chunk_output_type: console
---
<style>
body
  { counter-reset: source-line 0; }
pre.numberSource code
  { counter-reset: none; }
</style>


```{r, echo = FALSE}
# set working directory as project directory or one directory above,
rootdir <- try(rprojroot::find_rstudio_root_file(), silent = TRUE)
if (is(rootdir, "try-error")) rootdir <-  ".."
knitr::opts_knit$set(root.dir = rootdir)
```

```{r add link to github repo if any, echo = FALSE, results='asis'}

# print link to github repo if any
if (file.exists("./.git/config")){
  config <- readLines("./.git/config")
  url <- grep("url",  config, value = TRUE)
  url <- gsub("\\turl = |.git$", "", url)
  cat("\nSource code and data found at [", url, "](", url, ")", sep = "")
  }

```

```{r setup style, echo = FALSE, message = FALSE, warning=FALSE}

# options to customize chunk outputs
knitr::opts_chunk$set(
  class.source = "numberLines lineAnchors", # for code line numbers
  tidy.opts = list(width.cutoff = 65), 
  tidy = TRUE,
  message = FALSE
 )

# to add copy button to code blocks
htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "<i class=\"fa fa-clipboard\"></i>",
    success_text = "<i class=\"fa fa-check\" style=\"color: #90BE6D\"></i>",
    error_text = "<i class=\"fa fa-times-circle\" style=\"color: #F94144\"></i>"
  ),
  rmarkdown::html_dependency_font_awesome()
)

```

## Load packages
```{r packages, message = FALSE, warning = FALSE, echo = TRUE, eval = TRUE}

## add 'developer' to packages to be installed from github
x <- c("remotes", "lubridate", "readxl", "pbapply", "viridis", "ggplot2", "kableExtra", "knitr", "formatR", "MASS", "sp", "GGally", "brms", "lme4", "dplyr", "purrr", "forcats", "tidyr", "modelr", "tidybayes", "cowplot", "ggrepel", "posterior", "ggridges", "maRce10/PhenotypeSpace")

source("~/Dropbox/R_package_testing/sketchy/R/load_packages.R")
load_packages(x)

source("~/Dropbox/R_package_testing/brmsish/R/html_summary.R")
source("~/Dropbox/R_package_testing/brmsish/R/helpers.R")
source("~/Dropbox/R_package_testing/brmsish/R/read_summary.R")
source("~/Dropbox/R_package_testing/brmsish/R/check_rds_models.R")

```

## Functions and global parameters
```{r functions and parameters, eval = TRUE, echo = TRUE}

opts_knit$set(root.dir = "..")

# set evaluation false
opts_chunk$set(fig.width = 10, fig.height = 6, warning = FALSE, message = FALSE, tidy = TRUE)

read_excel_df <- function(...) data.frame(read_excel(...))


# for reading months in english format
sl <- Sys.setlocale(locale = "en_US.UTF-8")


standard_error <- function(x) sd(x)/sqrt(length(x))

cols <- viridis(10, alpha = 0.7)

col_pointrange <- cols[7]  
```

```{r read detections and prepare data, eval = TRUE}

# read ext sel tab calls
sels <- read.csv("./data/processed/tailored_budgie_calls_sel_tab.csv")

# keep only spectrographic parameters
sels <- sels[ , c("sound.files", "selec", "duration", "meanfreq", "sd", "freq.median", "freq.IQR", "time.IQR", "skew",  "kurt", "sp.ent", "time.ent", "entropy", "meandom", "mindom", "maxdom", "dfrange",  "modindx", "meanpeakf")]

sels$ID <- sapply(sels$sound.files, function(x) strsplit(x, "_")[[1]][1])
sels$month <- sapply(sels$sound.files, function(x) strsplit(x, "_")[[1]][2])
sels$day <- sapply(sels$sound.files, function(x) strsplit(x, "_")[[1]][3])
sels$year <- sapply(sels$sound.files, function(x) strsplit(x, "_")[[1]][4])

sels$date <- paste(sels$day, substr(sels$month, 0, 3), sels$year, sep = "-")

sels$date <- as.Date(sels$date, format = "%d-%b-%Y")

# acoustic measurements
areas_by_week <- readRDS("./data/processed/acoustic_space_area_by_individual_and_week.RDS")

indiv_ovlp <- readRDS("./data/processed/acoustic_space_density_overlap_to_first_week_by_individual.RDS")

indiv_ovlp$treatment <- factor(indiv_ovlp$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

group_ovlp <- readRDS("./data/processed/acoustic_space_density_overlap_to_group_by_week.RDS")

# group_ovlp <- do.call(rbind, lapply(unique(group_ovlp$ID), function(x) {
# 
#     X <- group_ovlp[group_ovlp$ID == x, ]
#     X$overlap.to.group <- X$overlap.to.group - X$overlap.to.group[X$week == min(as.numeric(as.character(X$week)))]
#     X$distance.to.group <- X$distance.to.group - X$distance.to.group[X$week == min(as.numeric(as.character(X$week)))]
#     return(X)
# }))

group_ovlp$treatment <- factor(group_ovlp$treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

```

## Counts per individual
```{r read detections and prepare data counts, eval = TRUE, results='asis'}

df <- as.data.frame(table(sels$ID))

names(df) <- c("ID", "Sample_size")

df <- df[order(df$Sample_size, decreasing = FALSE), ]

kb <-kable(df, row.names = FALSE) 
  
kb <- kable_styling(kb, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
  
print(kb)

```

## Add metadata
```{r, eval = TRUE}

metadat <- read_excel_df("./data/raw/INBREStress_MasterDataSheet_14Nov19.xlsx")

# head(metadat)

sels$ID[sels$ID == "125YGMM"] <- "125YGHM"
sels$ID[sels$ID == "394YBHM"] <- "394WBHM"

# setdiff(sels$ID, metadat$Bird.ID) setdiff(metadat$Bird.ID, sels$ID)

sels$treatment <- sapply(1:nrow(sels), function(x) {

    metadat$Treatment[metadat$Bird.ID == sels$ID[x]][1]

})


sels$treatment.room <- sapply(1:nrow(sels), function(x) {

    metadat$Treatment.Room[metadat$Bird.ID == sels$ID[x]][1]

})


sels$round <- sapply(1:nrow(sels), function(x) {

    metadat$Round[metadat$Bird.ID == sels$ID[x]][1]

})

sels$source.room <- sapply(1:nrow(sels), function(x) {

    metadat$Source.Room[metadat$Bird.ID == sels$ID[x]][1]

})

sels$record.group <- sapply(1:nrow(sels), function(x) {

    metadat$Record.Group[metadat$Bird.ID == sels$ID[x]][1]

})


# add week
out <- lapply(unique(sels$round), function(x) {

    Y <- sels[sels$round == x, ]

    min_date <- min(Y$date)
    week_limits <- min_date + seq(0, 100, by = 7)

    Y$week <- NA
    for (i in 2:length(week_limits)) Y$week[Y$date >= week_limits[i - 1] & Y$date <
        week_limits[i]] <- i - 1

    return(Y)
})

sels <- do.call(rbind, out)


sels$cort.baseline <- sapply(1:nrow(sels), function(x) {

    if (sels$week[x] == 1)
        out <- metadat$D3.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 2)
        out <- metadat$D7.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 3)
        out <- metadat$D14.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 4)
        out <- metadat$D21.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 5)
        out <- metadat$D28.CORT.Baseline[metadat$Bird.ID == sels$ID[x]][1]

    return(out)
})


sels$cort.stress <- sapply(1:nrow(sels), function(x) {

    if (sels$week[x] == 1)
        out <- metadat$D3.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 2)
        out <- metadat$D7.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 3)
        out <- metadat$D14.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 4)
        out <- metadat$D21.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 5)
        out <- metadat$D28.CORT.Stress[metadat$Bird.ID == sels$ID[x]][1]

    return(out)
})

sels$stress.response <- sels$cort.stress #- sels$cort.baseline

sels$weight <- sapply(1:nrow(sels), function(x) {

    if (sels$week[x] == 1)
        out <- metadat$D3.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 2)
        out <- metadat$D7.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 3)
        out <- metadat$D14.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 4)
        out <- metadat$D21.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 5)
        out <- metadat$D28.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    return(out)
})


sels$breath.count <- sapply(1:nrow(sels), function(x) {

    if (sels$week[x] == 1)
        out <- metadat$D3.Breath.Count[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 2)
        out <- metadat$D7.Breath.Count[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 3)
        out <- metadat$D14.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 4)
        out <- metadat$D21.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    if (sels$week[x] == 5)
        out <- metadat$D28.Bird.Weight..g.[metadat$Bird.ID == sels$ID[x]][1]

    return(out)
})


# remove week 5
sels <- sels[sels$week != 5, ]

```

```{r prepare data for stats, eval = TRUE}

agg_dat <- aggregate(selec ~ ID + week, data = sels, length)

# compare to week 1 agg_dat$call.count <- sapply(1:nrow(agg_dat), function(x) {
# baseline <- agg_dat$selec[agg_dat$week == 1 & agg_dat$ID == agg_dat$ID[x]] if
# (length(baseline) > 0) change <- agg_dat$selec[x] - baseline else change <-
# agg_dat$selec[x] return(change) } )

# without comparing to week 1
agg_dat$call.count <- sapply(1:nrow(agg_dat), function(x) agg_dat$selec[x])

agg_dat$selec <- NULL

agg_dat$baseline.CORT <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$cort.baseline[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$cort.baseline[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})

agg_dat$stress.response <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$stress.response[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$stress.response[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})


agg_dat$stress.CORT <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$cort.stress[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$cort.stress[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})

agg_dat$weight <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$weight[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$weight[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})

agg_dat$breath.rate <- sapply(1:nrow(agg_dat), function(x) {

    baseline <- sels$breath.count[sels$week == 1 & sels$ID == agg_dat$ID[x]]
    current <- sels$breath.count[sels$week == agg_dat$week[x] & sels$ID == agg_dat$ID[x]]

    if (length(baseline) > 0 & length(current) > 0)
        change <- mean(current) - mean(baseline) else change <- NA

    return(change)
})

agg_dat$acoustic.diversity <- sapply(1:nrow(agg_dat), function(x) {

    area <- areas_by_week$raref.area[areas_by_week$ID == agg_dat$ID[x] & areas_by_week$week ==
        agg_dat$week[x]]

    if (length(area) < 1)
        area <- NA

    return(area)
})

agg_dat$acoustic.distance <- sapply(1:nrow(agg_dat), function(x) {

    distance <- indiv_ovlp$distance.to.first.week[indiv_ovlp$ID == agg_dat$ID[x] &
        indiv_ovlp$week == agg_dat$week[x]]

    if (length(distance) < 1)
        distance <- NA

    return(distance)
})

agg_dat$acustic.plasticity <- sapply(1:nrow(agg_dat), function(x) {

    overlap <- indiv_ovlp$overlap.to.first.week[indiv_ovlp$ID == agg_dat$ID[x] &
        indiv_ovlp$week == agg_dat$week[x]]

    plasticity <- 1 - overlap
    
    if (length(plasticity) < 1)
        plasticity <- NA

    return(plasticity)
})

agg_dat$acoustic.convergence <- sapply(1:nrow(agg_dat), function(x) {

    overlap <- group_ovlp$overlap.to.group[group_ovlp$ID == agg_dat$ID[x] & group_ovlp$week ==
        agg_dat$week[x]]

    if (length(overlap) < 1)
        overlap <- NA

    return(overlap)
})


agg_dat$treatment <- sapply(1:nrow(agg_dat), function(x) unique(sels$treatment[sels$ID ==
    agg_dat$ID[x]]))

agg_dat$round <- sapply(1:nrow(agg_dat), function(x) unique(sels$round[sels$ID ==
    agg_dat$ID[x]]))


```

# Physiological parameters

Barplot and effect sizes graph
```{r, eval = TRUE, out.width="120%", out.height="200%"}

physio_models <- readRDS("./data/processed/physiological_response_models.RDS")

breath.count <- stack(metadat[, c("D3.Breath.Count", "D7.Breath.Count", "D14.Breath.Count",
    "D21.Breath.Count", "D28.Breath.Count")])

weight <- stack(metadat[, c("D3.Bird.Weight..g.", "D7.Bird.Weight..g.", "D14.Bird.Weight..g.",
    "D21.Bird.Weight..g.", "D28.Bird.Weight..g.")])

cort.stress <- stack(metadat[, c("D3.CORT.Stress", "D7.CORT.Stress", "D14.CORT.Stress",
    "D21.CORT.Stress", "D28.CORT.Stress")])

cort.baseline <- stack(metadat[, c("D3.CORT.Baseline", "D7.CORT.Baseline", "D14.CORT.Baseline",
    "D21.CORT.Baseline", "D28.CORT.Baseline")])


stress <- data.frame(metadat[, c("Bird.ID", "Treatment", "Round", "Treatment.Room")],
    week = breath.count$ind, breath.count = breath.count$values, weight = weight$values,
    cort.stress = cort.stress$values, cort.baseline = cort.baseline$values, stress.response = cort.stress$values -
        cort.baseline$values)

# head(stress)

stress$week <- factor(sapply(strsplit(as.character(stress$week), "\\."), "[[", 1),
    levels = c("D3", "D7", "D14", "D21", "D28"))

stress$day <- as.numeric(gsub("D", "", as.character(stress$week)))
stress$round <- paste("Round", stress$Round)

stress$treatment <- factor(stress$Treatment, levels = c("Control", "Medium Stress",
    "High Stress"))

# remove 5th week
stress <- stress[stress$week != "D28", ]


stress_l <- lapply(stress$Bird.ID, function(x) {
    X <- stress[stress$Bird.ID == x, ]

    X$breath.count <- X$breath.count - X$breath.count[X$week == "D3"]
    X$weight <- X$weight - X$weight[X$week == "D3"]
    X$cort.stress <- X$cort.stress - X$cort.stress[X$week == "D3"]
    X$cort.baseline <- X$cort.baseline - X$cort.baseline[X$week == "D3"]
    X$stress.response <- X$stress.response - X$stress.response[X$week == "D3"]

    return(X)
})

stress <- do.call(rbind, stress_l)

agg_stress <- aggregate(cbind(breath.count, weight, stress.response, cort.baseline) ~ week + treatment, stress, mean)
agg_stress_se <- aggregate(cbind(breath.count, weight, stress.response, cort.baseline) ~ week + treatment, stress, standard_error)

names(agg_stress_se) <- paste(names(agg_stress_se), ".se", sep = "")

agg_stress <- cbind(agg_stress, agg_stress_se[ , 3:6])

agg_stress$Week <- 1:4

bs <- 10

gg_breath.count <- ggplot(data = agg_stress, aes(x = Week, y = breath.count, fill = treatment)) + 
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = breath.count - breath.count.se, ymax = breath.count + breath.count.se), width = 0.1) +
scale_fill_viridis_d(begin = 0.1, end = 0.9) + 
    facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Mean change in breath\nrate (breaths/min)", x = "Week") + 
    theme_classic(base_size = bs) + 
    theme(legend.position = "none")

gg_weight <- ggplot(data = agg_stress, aes(x = Week, y = weight, fill = treatment)) + 
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = weight - weight.se, ymax = weight + weight.se), width = 0.1) +
    scale_fill_viridis_d(begin = 0.1, end = 0.9) + 
    facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Mean change in \nweight (grams)", x = "Week") + 
    theme_classic(base_size = bs) + 
    theme(legend.position = "none")


gg_cort.baseline <- ggplot(data = agg_stress, aes(x = Week, y = cort.baseline, fill = treatment)) + 
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = cort.baseline - cort.baseline.se, ymax = cort.baseline + cort.baseline.se), width = 0.1) +
    scale_fill_viridis_d(begin = 0.1, end = 0.9) +
    facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Mean change in\nbaseline CORT (ng/mL)", x = "Week") + 
    theme_classic(base_size = bs) + 
    theme(legend.position = "none")


gg_stress.response <- ggplot(data = agg_stress, aes(x = Week, y = stress.response, fill = treatment)) + 
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = stress.response - stress.response.se, ymax = stress.response + stress.response.se), width = 0.1) +
    scale_fill_viridis_d(begin = 0.1, end = 0.9) + 
    facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Mean change in stress response \nCORT (ng/mL)", x = "Week") +
    theme_classic(base_size = bs) + 
    theme(legend.position = "none")


gg_coeffs_physio <- lapply(physio_models, function(x){
    
    vars <- grep("b_", posterior::variables(x), value = TRUE)
    draws <- posterior::as_draws_array(x, variable = vars)

    coef_table <- draw_summary(draws, variables = vars, probs = c(0.025, 0.975), robust = TRUE)
    
    coef_table$predictor <- rownames(coef_table)
    coef_table$predictor <- gsub("b_treatment|b_", "", coef_table$predictor)
    coef_table$predictor <- gsub("Stress", " stress", coef_table$predictor)
    coef_table$predictor <- gsub("week", "Week", coef_table$predictor)
    coef_table <- coef_table[coef_table$predictor != "Intercept", ]
    
gg_coef <- ggplot2::ggplot(data = coef_table, aes(x = Estimate, y = predictor)) +
    geom_vline(xintercept = 0, lty = 2) +
    ggplot2::geom_point(size = 4, col = col_pointrange) +
    ggplot2::geom_errorbar(ggplot2::aes(xmin = `l-95% CI`, xmax = `u-95% CI`),
                             width = 0, col = col_pointrange) +
      ggplot2::theme_classic(base_size = bs) +
      ggplot2::theme(
        axis.ticks.length = ggplot2::unit(0, "pt"),
        plot.margin = ggplot2::margin(0, 0, 0, 0, "pt"),
        legend.position = "none",
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank()
      ) +
      ggplot2::labs(x = "Effect size", y = "")

      return(gg_coef)  
})

cowplot::plot_grid(
    gg_breath.count,
    gg_weight, 
    gg_cort.baseline,
    gg_stress.response, 
    gg_coeffs_physio[[grep("breath", names(gg_coeffs_physio))]] + theme_classic(base_size = bs), 
    gg_coeffs_physio[[grep("weight", names(gg_coeffs_physio))]] + theme_classic(base_size = bs),
    gg_coeffs_physio[[grep("baseline", names(gg_coeffs_physio))]] + theme_classic(base_size = bs),
    gg_coeffs_physio[[grep("response", names(gg_coeffs_physio))]] + theme_classic(base_size = bs), nrow = 2, rel_heights = c(1.8, 1))

# try bs = 20 for saving plots

# cowplot::ggsave2(filename = "./output/bar_graphs_and_estimates_physiology_70dpi.jpeg", width = 25, height = 9)
# 
# cowplot::ggsave2(filename = "./output/bar_graphs_and_estimates_physiology_300dpi.jpeg", dpi = 300, width = 25, height = 9)

```

## Stats

Models: Predicted physio measure ~ treatment + week (continuous) + IndRandom

Variables (Difference from Week 1): weight, BR, baseline CORT, Stress CORT, Stress Response 

```{r, eval = FALSE}

responses <- c("baseline.CORT", "stress.response", "stress.CORT", "weight", "breath.rate")

predictors <- c("~ treatment + week + (1|ID) + (1|round)")

formulas <- expand.grid(responses = responses, predictors = predictors, stringsAsFactors = FALSE)

vars_to_scale <- c(responses, "week")

# remove week 1
sub_agg_dat <- agg_dat[agg_dat$week != 1, ]

for (i in vars_to_scale) sub_agg_dat[, vars_to_scale] <- scale(sub_agg_dat[, vars_to_scale])

physio_models <- lapply(1:nrow(formulas), function(x) {

    sub_dat <- sub_agg_dat[!is.na(sub_agg_dat[names(sub_agg_dat) == formulas$responses[x]]),
        ]
    sub_dat

    mod <- brm(formula = paste(formulas$responses[x], formulas$predictors[x]),
        iter = 20000, silent = 2, data = sub_dat, control = list(adapt_delta = 0.9),
        chains = 4,
        prior = c(prior(normal(0, 5), "b"), prior(normal(0, 10), "Intercept"),
    prior(student_t(3, 0, 10), "sd"), prior(student_t(3, 0, 10), "sigma")))

    return(mod)
})


names(physio_models) <- paste(formulas$responses, formulas$predictors)

saveRDS(physio_models, "./data/processed/physiological_response_models.RDS")

```

```{r, results = 'asis'}

physio_models <- readRDS("./data/processed/physiological_response_models.RDS")

for (x in 1:length(physio_models)) 
    html_summary(physio_models[[x]], gsub.pattern = "b_treatment|b_", gsub.replacement = "", highlight = FALSE, remove.intercepts = TRUE, model.name = names(physio_models)[x])
   
```

&nbsp;



<div class="alert alert-info">

## Takeaways

-  Breath rate decreases gradually with time across after the first week

-  Stress response is higher in "high stress" birds compared to first week

</div>

&nbsp;

# Acoustic space projection

t-SNE
```{r calculate tsne, eval = FALSE}

scale_param <- scale(sels[, c("duration", "meanfreq", "sd", "freq.median", "freq.IQR",
    "time.IQR", "skew", "kurt", "sp.ent", "time.ent", "entropy", "meandom", "mindom",
    "maxdom", "dfrange", "modindx", "meanpeakf")])

tsne <- Rtsne(scale_param, dims = 2, perplexity = 30, verbose = FALSE, max_iter = 5000)

saveRDS(tsne, "./data/processed/tsne_on_acoustic_parameters_jun_2021.RDS")
```

```{r plot tsne, eval = TRUE}

tsne <- readRDS("./data/processed/tsne_on_acoustic_parameters_jun_2021.RDS")

Y <- as.data.frame(tsne$Y)
names(Y) <- c("TSNE1", "TSNE2")

sels <- data.frame(sels, Y)

sels$treatment <- factor(sels$treatment, levels = c("Control", "Medium Stress", "High Stress"))

ggplot(sels, aes(x = TSNE1, y = TSNE2, col = as.factor(treatment))) + geom_point() +
    labs(color = "Treatment") + scale_color_viridis_d(alpha = 0.4) + theme_classic(base_size = 25) + 
    guides(colour = guide_legend(override.aes = list(size = 10)))
```


# Behavioral parameters


Barplot and effect sizes pgrah
```{r, eval = TRUE, out.width="120%", out.height="200%"}

behav_models <- readRDS("./data/processed/behavioral_response_models.RDS")

agg_call.count <- aggregate(cbind(call.count, acoustic.convergence) ~ week + treatment, agg_dat, mean)

agg_behav <- aggregate(cbind(acoustic.diversity, acustic.plasticity) ~ week + treatment, agg_dat, mean)

agg_call.count_se <- aggregate(cbind(call.count, acoustic.convergence) ~ week + treatment, agg_dat, standard_error)

agg_behav_se <- aggregate(cbind(acoustic.diversity, acustic.plasticity) ~ week + treatment, agg_dat, standard_error)

agg_behav_se <- merge(agg_call.count_se, agg_behav_se, all = TRUE)

names(agg_behav_se) <- paste(names(agg_behav_se), ".se", sep = "")

agg_behav <- merge(agg_call.count, agg_behav, all = TRUE)

agg_behav <- cbind(agg_behav, agg_behav_se[ , 3:6])

bs <- 10

agg_behav$treatment <- factor(agg_behav$treatment, levels = c("Control", "Medium Stress",
"High Stress"))

gg_call.count <- ggplot(data = agg_behav, aes(x = week, y = call.count, fill = treatment)) + 
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = call.count - call.count.se, ymax = call.count + call.count.se), width = 0.1) +
scale_fill_viridis_d(begin = 0.1, end = 0.9) + 
    facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Vocal output", x = "Week") + 
    theme_classic(base_size = bs) + 
    theme(legend.position = "none")

gg_acoustic.diversity <- ggplot(data = agg_behav, aes(x = week, y = acoustic.diversity, fill = treatment)) + 
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = acoustic.diversity - acoustic.diversity.se, ymax = acoustic.diversity + acoustic.diversity.se), width = 0.1) +
    scale_fill_viridis_d(begin = 0.1, end = 0.9) + 
    facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Change in vocal diversity", x = "Week") + 
    theme_classic(base_size = bs) + 
    theme(legend.position = "none")

gg_acustic.plasticity <- ggplot(data = agg_behav, aes(x = week, y = acustic.plasticity, fill = treatment)) + 
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = acustic.plasticity - acustic.plasticity.se, ymax = acustic.plasticity + acustic.plasticity.se), width = 0.1) +
    scale_fill_viridis_d(begin = 0.1, end = 0.9) + 
    facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Vocal plasticity", x = "Week") + 
    theme_classic(base_size = bs) + 
    theme(legend.position = "none")

gg_acoustic.convergence <- ggplot(data = agg_behav, aes(x = week, y = acoustic.convergence, fill = treatment)) + 
    geom_bar(stat = "identity") +
    geom_errorbar(aes(ymin = acoustic.convergence - acoustic.convergence.se, ymax = acoustic.convergence + acoustic.convergence.se), width = 0.1) +
    scale_fill_viridis_d(begin = 0.1, end = 0.9) + 
    facet_wrap(~treatment, ncol = 3, scale = "fixed") +
    labs(y = "Vocal convergence", x = "Week") + 
    theme_classic(base_size = bs) + 
    theme(legend.position = "none")

gg_coeffs_behav <- lapply(behav_models, function(x){
    
    vars <- grep("b_", posterior::variables(x), value = TRUE)
    draws <- posterior::as_draws_array(x, variable = vars)

    coef_table <- draw_summary(draws, variables = vars, probs = c(0.025, 0.975), robust = TRUE)
    
    coef_table$predictor <- rownames(coef_table)
    coef_table$predictor <- gsub("b_treatment|b_", "", coef_table$predictor)
    coef_table$predictor <- gsub("Stress", " stress", coef_table$predictor)
    coef_table$predictor <- gsub("week", "Week", coef_table$predictor)
    coef_table <- coef_table[coef_table$predictor != "Intercept", ]
    
gg_coef <- ggplot2::ggplot(data = coef_table, aes(x = Estimate, y = predictor)) +
    geom_vline(xintercept = 0, lty = 2) +
    ggplot2::geom_point(size = 4, col = col_pointrange) +
    ggplot2::geom_errorbar(ggplot2::aes(xmin = `l-95% CI`, xmax = `u-95% CI`),
                             width = 0, col = col_pointrange) +
      ggplot2::theme_classic(base_size = bs) +
      ggplot2::theme(
        axis.ticks.length = ggplot2::unit(0, "pt"),
        plot.margin = ggplot2::margin(0, 0, 0, 0, "pt"),
        legend.position = "none",
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank()
      ) +
      ggplot2::labs(x = "Effect size", y = "")

      return(gg_coef)  
})

cowplot::plot_grid(
    gg_call.count,
    gg_acoustic.diversity, 
    gg_acustic.plasticity,
    gg_acoustic.convergence, 
    gg_coeffs_behav[[grep("count", names(gg_coeffs_behav))]] + theme_classic(base_size = bs), 
    gg_coeffs_behav[[grep("diversity", names(gg_coeffs_behav))]] + theme_classic(base_size = bs),
    gg_coeffs_behav[[grep("plasticity", names(gg_coeffs_behav))]] + theme_classic(base_size = bs),
    gg_coeffs_behav[[grep("convergence", names(gg_coeffs_behav))]] + theme_classic(base_size = bs), nrow = 2, rel_heights = c(1.8, 1))

# try bs = 20 for saving plots

# cowplot::ggsave2(filename = "./output/bar_graphs_and_estimates_behavior_70dpi.jpeg", width = 25, height = 9)
# # 
# cowplot::ggsave2(filename = "./output/bar_graphs_and_estimates_behavior_300dpi.jpeg", dpi = 300, width = 25, height = 9)

```

## Stats

Model: Predicted behavior ~ treatment + week (continuous) + IndRandom

Variables: # calls, Distance moved from self in first week, Overlap to original acoustic space, Match to group repertoire, Maybe overall size of acoustic space

Do as comparison to week one using rarefacted calls and kernel density


```{r, eval = FALSE}

responses <- c("call.count", "acoustic.diversity", "acustic.plasticity", "acoustic.convergence")

predictors <- c("~ treatment + week + (1|ID) + (1|round)")

formulas <- expand.grid(responses = responses, predictors = predictors, stringsAsFactors = FALSE)

vars_to_scale <- c(responses, "week")


for (i in vars_to_scale) agg_dat[, vars_to_scale] <- scale(agg_dat[, vars_to_scale])

behav_models <- lapply(1:nrow(formulas), function(x) {

    sub_dat <- agg_dat[!is.na(agg_dat[names(agg_dat) == formulas$responses[x]]),]

    # remove week 1
    if (!grepl("count|group", formulas$responses[x]))
        sub_dat <- sub_dat[sub_dat$week != 1, ] 

    mod <- brm(formula = paste(formulas$responses[x], formulas$predictors[x]),
        iter = 50000, silent = 2, data = sub_dat, control = list(adapt_delta = 0.9, max_treedepth = 15),
        chains = 4, prior = c(prior(normal(0, 5), "b"), prior(normal(0, 10), "Intercept"),
    prior(student_t(3, 0, 10), "sd"), prior(student_t(3, 0, 10), "sigma"))
)

        return(mod)
})


names(behav_models) <- paste(formulas$responses, formulas$predictors)

saveRDS(behav_models, "./data/processed/behavioral_response_models.RDS")

```

```{r, results = 'asis'}

behav_models <- readRDS("./data/processed/behavioral_response_models.RDS")


for (x in 1:length(behav_models)) 
    html_summary(behav_models[[x]], gsub.pattern = "b_treatment|b_", gsub.replacement = "", highlight = FALSE, remove.intercepts = TRUE, model.name = names(behav_models)[x])
   
```

&nbsp;

<div class="alert alert-info">

## Takeaways

-  Higher vocal output in "high stress" birds compared to control

-  Higher acoustic overlap to themselves in week 1 for "high stress" birds compared to control

-  Decrease in overlap to themselves in week 1 across time

</div>

&nbsp;


# Combined model diagnostics

```{r, eval = TRUE, results='asis'}

check_rds_models(path = "./data/processed", html = TRUE, verbose = FALSE)

```

---

<font size="4">Session information</font>

```{r session info, echo=F, eval = TRUE}

sessionInfo()

```